Supervised Learning for Psychological Attention to High School Students

### 2020-11-18 article/article.tex
[ article ] Finished formatting appendix and file.

\begin{table}
  \centering
  \caption{Performance scores for $\mathcal{L}=[1,2,3]$ and $\eta=0.9$.}
  \label{tab:L123}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & 0 & 1 \\
    Testing & 0 & 1 \\
    Validation & 0 & 1 \\ \hline
  \end{tabular}
\end{table}

\begin{table}
  \centering
  \caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.9$.}
  \label{tab:L2}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & $\times$ & 1 \\
    Testing & $\times$ & 1 \\
    Validation & $\times$ & 1 \\ \hline
  \end{tabular}
\end{table}

\begin{table}
  \centering
  \caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.9$.}
  \label{tab:L3}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & 0.5 & 1 \\
    Testing & $\times$ & 1 \\
    Validation & 1 & 1 \\ \hline
  \end{tabular}
\end{table}

@@

@@

\printbibliography

\newpage
\appendices

@@

\subsection{Support Vector Machines}
The PAC learning, results using the same optimization-sensitivity methodology,
are presented in Fig. \ref{fig:error-SVM-emb}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-emb-linear-error.pdf}
        \caption{Linear SVM.}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-emb-poly-error.pdf}
        \caption{Polynomial SVM}
    \end{subfigure}
    \caption{Estimated $\epsilon$ for different training set sizes.}
    \label{fig:error-SVM-emb}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/svm-emb-linear-contour-0-1.pdf}
  \caption{Linear kernel SVM contour with real labels.}
\end{figure}

\begin{table}
\centering
\caption{Performance scores for linear SVM.}
\label{tab:linear_SVM_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for polynomial SVM.}
\label{tab:poly_SVM_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for polynomial RBF.}
\label{tab:rbf_SVM_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for DT.}
\label{tab:DT_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 1 & 1 \\
Testing & 0 & 1 \\
Validation & 0.63 & 0.94 \\ \hline
\end{tabular}
\end{table}

\subsection{Neural Networks}
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[2,3,3]$ network with $\eta=0.9$
    (worst).}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.5-emb-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.5-emb-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/3-0.5-emb-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[3]$ with $\eta=0.5$ network
    (2nd best).}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.2-emb-gradients.pdf}
        \caption{Gradients for each layer.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.2-emb-error.pdf}
        \caption{Average error energy per epoch.}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/2-0.2-emb-roc.pdf}
        \caption{ROC curve.}
    \end{subfigure}
    \caption{Learning curves for $\mathcal{L}=[2]$ with $\eta=0.2$ network
    (best).}
\end{figure*}

\begin{table}
\centering
\caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.2$.}
\label{tab:L2_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & $\times$ & 1 \\
Testing & $\times$ & 1 \\
Validation & $\times$ & 1 \\ \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.5$.}
\label{tab:L3_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & $\times$ & 1 \\
Testing & $\times$ & 1 \\
Validation & $\times$ & 1 \\ \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Performance scores for $\mathcal{L}=[2,3,3]$ and $\eta=0.9$.}
\label{tab:L233_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
  \centering
  \caption{Performance scores for $\mathcal{L}=[1,2,3]$ and $\eta=0.9$.}
  \label{tab:L123}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & 0 & 1 \\
    Testing & 0 & 1 \\
    Validation & 0 & 1 \\ \hline
  \end{tabular}
\end{table}

\begin{table}[H]
  \centering
  \caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.9$.}
  \label{tab:L2}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & $\times$ & 1 \\
    Testing & $\times$ & 1 \\
    Validation & $\times$ & 1 \\ \hline
  \end{tabular}
\end{table}

\begin{table}[H]
  \centering
  \caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.9$.}
  \label{tab:L3}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & 0.5 & 1 \\
    Testing & $\times$ & 1 \\
    Validation & 1 & 1 \\ \hline
  \end{tabular}
\end{table}

@@

The machine that had the best performance was the Decision Tree, in comparison
to the SVMs and the NNs. This happened because the other machines try to
separate the data using all the given information, meanwhile the Decision Tree
realizes that the other variables do not give any crucial data for separating.
Furthermore, the variable ``Emotional Socialization'' is the most important for
classifying data.

@@

\newpage
\printbibliography

\clearpage
\appendices

@@

\subsection{Support Vector Machines}
The PAC learning, results using the same optimization-sensitivity methodology,
are presented in Figs. \ref{fig:error-SVM-emb}, \ref{fig:error-SVM-emb2}.

\newpage

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/svm-emb-linear-error.pdf}
  \caption{Estimated $\epsilon$ for different training set sizes (Linear SVM).}
  \label{fig:error-SVM-emb}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/svm-emb-poly-error.pdf}
  \caption{Estimated $\epsilon$ for different training set sizes (Poly SVM).}
  \label{fig:error-SVM-emb2}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/svm-emb-linear-contour-0-1.pdf}
  \caption{Linear kernel SVM contour with real labels.}
\end{figure}

\begin{table}[H]
  \centering
  \caption{Performance scores for linear SVM.}
  \label{tab:linear_SVM_emb}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & 0 & 1 \\
    Testing & 0 & 1 \\
    Validation & 0 & 1 \\ \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{Performance scores for polynomial SVM.}
  \label{tab:poly_SVM_emb}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & 0 & 1 \\
    Testing & 0 & 1 \\
    Validation & 0 & 1 \\ \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{Performance scores for polynomial RBF.}
  \label{tab:rbf_SVM_emb}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & 0 & 1 \\
    Testing & 0 & 1 \\
    Validation & 0 & 1 \\ \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{Performance scores for DT.}
  \label{tab:DT_emb}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & 1 & 1 \\
    Testing & 0 & 1 \\
    Validation & 0.63 & 0.94 \\ \hline
  \end{tabular}
\end{table}

\subsection{Neural Networks}
\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-gradients.pdf}
    \caption{Gradients for each layer.}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-error.pdf}
    \caption{Average error energy per epoch.}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-roc.pdf}
    \caption{ROC curve.}
  \end{subfigure}
  \caption{Learning curves for $\mathcal{L}=[2,3,3]$ network with $\eta=0.9$
    (worst).}
\end{figure*}

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/3-0.5-emb-gradients.pdf}
    \caption{Gradients for each layer.}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/3-0.5-emb-error.pdf}
    \caption{Average error energy per epoch.}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/3-0.5-emb-roc.pdf}
    \caption{ROC curve.}
  \end{subfigure}
  \caption{Learning curves for $\mathcal{L}=[3]$ with $\eta=0.5$ network (2nd
    best).}
\end{figure*}

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/2-0.2-emb-gradients.pdf}
    \caption{Gradients for each layer.}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/2-0.2-emb-error.pdf}
    \caption{Average error energy per epoch.}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/2-0.2-emb-roc.pdf}
    \caption{ROC curve.}
  \end{subfigure}
  \caption{Learning curves for $\mathcal{L}=[2]$ with $\eta=0.2$ network
    (best).}
\end{figure*}

\begin{table}[H]
  \centering
  \caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.2$.}
  \label{tab:L2_emb}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & $\times$ & 1 \\
    Testing & $\times$ & 1 \\
    Validation & $\times$ & 1 \\ \hline
  \end{tabular}
\end{table}

\begin{table}[H]
  \centering
  \caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.5$.}
  \label{tab:L3_emb}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & $\times$ & 1 \\
    Testing & $\times$ & 1 \\
    Validation & $\times$ & 1 \\ \hline
  \end{tabular}
\end{table}

\begin{table}[H]
  \centering
  \caption{Performance scores for $\mathcal{L}=[2,3,3]$ and $\eta=0.9$.}
  \label{tab:L233_emb}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
    Training & 0 & 1 \\
    Testing & 0 & 1 \\
    Validation & 0 & 1 \\ \hline
  \end{tabular}
\end{table}
